Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 15

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the  exponential convergence of solutions. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

>>>>

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.
